\chapter{Library requirements}\label{C:lib}

This Chapter describes some things done to be in accordance with the `Library Requirements for the Deposit of Theses' booklet, which can be obtained from the VUW library.

\section{Font size}
\textit{12 point font is recommended.} 

Set this yourself with the \verb+12pt+ option to the document class.

\section{Single or double sided}
\textit{Typing on one side preferred, text on both sides acceptable for longer works.} 

Use the \verb+oneside+ or \verb+twoside+ option to the document class. The \textsf{book} class default is \verb+twoside+.


\section{Line spacing}
\textit{Lines should be double spaced, or at least 1.5 spaces apart.} 

1.5 spacing for 12 point is set using:
\begin{itemize}
\item \verb+\renewcommand{\baselinestretch}{1.24}+  
\end{itemize}

To set anything else use, e.g  \verb+\renewcommand{\baselinestretch}{1.0}+ in the preamble. See p 53 of \cite{GMS94} for more information.


\section{Margins}
\textit{Uniform margins of at least 4cm on binding side, other three sides to have at least 1.5 cm}

\LaTeX\ styles often leave a lot of white space, and \textsf{book} is no exception. We only have to worry about the binding side.

For \verb+twoside+ we use these settings:
\setlength{\textheight}{19.8cm}
\setlength{\oddsidemargin}{1.46cm}
\setlength{\evensidemargin}{0.83cm}

For \verb+oneside+, if we use:
\begin{verbatim}
\setlength{\textheight}{19.8cm}
\setlength{\oddsidemargin}{1.46cm}
\end{verbatim}

Then \textsf{book} gives a margin of 4cm on the binding side, and about 3.2cm elsewhere.

If you want to change these then use the \textsf{layout} package.

\section{Paper size}
\textit{High quality A4 paper, all pages of equal size}

Set this yourself with the \verb+a4paper+ option to the document class.